Pretty darn good control: when are approximate solutions better than approximate models

### 2023-01-25 manuscript/manuscript.Rmd
mini

```{r linear_tuning, fig.cap = "Result of the tuning procedure for the constant mortality strategy. (A) Mean episode reward (averaged over 50 episodes) shown as scatter data, $2\times$ standard deviation around each scatter point shown as a grey shade. Vertical lines correspond to the optimal constant mortality rate $F^* = 0.036$ (red) and $0.8 F^*=0.0288$ (green). (B) Several constant mortality policies shown for illustrative purposes. Slopes $0.02$, $0.03$, $0.055$ and $0.065$ shown in black; the optimal linear policy $F^*X$ shown in red, while $0.8F^*X$ shown in green.", out.width = "6.5in"}
msy_rewards <- msy |>
  group_by(action, rep) |>
  filter(t == max(t)) |> 
  group_by(action) |>
  summarise(mean_reward = mean(reward),
            sd = sd(reward))

@@

In Fig. \ref{fig:timeseries} we show one example time series for each of the three controls we analyzed: 
the left panel uses an optimalconstant mortality control $F^*X$, the middle panel uses $0.8 F^* X$, while the right panel is controlled by the trained DRL agent.
We see that that optimal constant mortality control leads to a near-extinction event at around $t=100$.
The constant mortality policy at $0.8 F^*$ is already conservative enough to support a sustainable path.
There, the population levels are maintained roughly in a stationary state.
Finally, the DRL time series shows an oscillatory behavior, with a slight dephase between the $Y$ and $Z$ curves, while the $X$ oscillations are roughly anticorrelated with $Z$.

```{r timeseries, fig.cap="TBD.", out.width = "6.5in"}
policy_labels <- list("msy" = "Opt. Const. Mortality", "tac"= "80% Opt. Const. Mortality", "ppo"= "DRL")
policy_labeller <- function(variable,value){
  return(policy_labels[value])
}
msy_tac_ppo |> 
    group_by(rep, policy) |>
    filter(rep == 2) |>
    ggplot(aes(t, abundance, col = species)) + 
        geom_line()  + 
        scale_color_manual(values=c('palegreen3', 'coral1', 'deepskyblue4')) +
        facet_wrap(~factor(policy, levels = c("msy", "tac", "ppo")), labeller = policy_labeller ) +
        labs(y = "abundance", x = "time") +
        theme(aspect.ratio = 2/3)
```

@@

```{r timeseries_old, fig.cap="TBD.", out.width = "6.5in"}
policy_labels <- list("msy" = "Opt. Const. Mortality", "tac"= "80% Opt. Const. Mortality", "ppo"= "DRL")
policy_labeller <- function(variable,value){
  return(policy_labels[value])
}
msy_tac_ppo |> 
    group_by(rep, policy) |>
    filter(rep == 2) |>
    ggplot(aes(t, abundance, col = species)) + 
        geom_line()  + 
        scale_color_manual(values=c('palegreen3', 'coral1', 'deepskyblue4')) +
        facet_wrap(~factor(policy, levels = c("msy", "tac", "ppo")), labeller = policy_labeller ) +
        labs(y = "abundance", x = "time") +
        theme(aspect.ratio = 2/3)
```

>>>>

```{r linear_tuning, fig.cap = "Result of the tuning procedure for the constant mortality strategy. (A) Mean episode reward (averaged over 50 episodes) shown as scatter data, and shaded in gray are two standard deviations around each scatter point. Vertical lines correspond to the optimal constant mortality rate $F^* = 0.036$ (red) and $0.8 F^*=0.0288$ (green). (B) Several constant mortality policies shown for illustrative purposes. Slopes $0.02$, $0.03$, $0.055$ and $0.065$ shown in black; the optimal linear policy $F^*X$ shown in red, while $0.8F^*X$ shown in green.", out.width = "6.5in"}
msy_rewards <- msy |>
  group_by(action, rep) |>
  filter(t == max(t)) |> 
  group_by(action) |>
  summarise(mean_reward = mean(reward),
            sd = sd(reward))

@@

In Fig. \ref{fig:timeseries} we show one example time series for each of the three controls we analyzed: 
the left panel uses an optimalconstant mortality control $F^*X$, the middle panel uses $0.8 F^* X$, while the right panel is controlled by the trained DRL agent.
We see that that optimal constant mortality control leads to a near-extinction event at around $t=150$.
The constant mortality policy at $0.8 F^*$ is already conservative enough to support a sustainable path.
There, the population levels are maintained roughly in a stationary state.
Finally, the DRL time series shows an oscillatory behavior, with a slight dephase between the $Y$ and $Z$ curves, while the $X$ oscillations are roughly anticorrelated with $Z$.

```{r timeseries, fig.cap="TBD.", out.width = "6.5in"}
policy_labels <- list("msy" = "Opt. Const. Mortality", "tac"= "80% Opt. Const. Mortality", "ppo"= "DRL")
policy_labeller <- function(variable,value){
  return(policy_labels[value])
}
msy_tac_ppo |> 
    group_by(rep, policy) |>
    filter(rep == 5) |>
    ggplot(aes(t, abundance, col = species)) + 
        geom_line()  + 
        scale_color_manual(values=c('palegreen3', 'coral1', 'deepskyblue4')) +
        facet_wrap(~factor(policy, levels = c("msy", "tac", "ppo")), labeller = policy_labeller ) +
        labs(y = "abundance", x = "time") +
        theme(aspect.ratio = 2/3)
```

@@

```{r timeseries_old, fig.cap="TBD.", out.width = "6.5in"}
policy_labels <- list("msy" = "Opt. Const. Mortality", "tac"= "80% Opt. Const. Mortality", "ppo"= "DRL")
policy_labeller <- function(variable,value){
  return(policy_labels[value])
}
msy_tac_ppo |> 
    group_by(rep, policy) |>
    filter(rep == 5) |>
    ggplot(aes(t, abundance, col = species)) + 
        geom_line()  + 
        scale_color_manual(values=c('palegreen3', 'coral1', 'deepskyblue4')) +
        facet_wrap(~factor(policy, levels = c("msy", "tac", "ppo")), labeller = policy_labeller ) +
        labs(y = "abundance", x = "time") +
        theme(aspect.ratio = 2/3)
```
